### 2019-05-28 doc/chapters/using_stainless.tex
fixed typos

\section{Configuration}
There are two ways to integrate Stainless in a Scala project, the scala build tool (abt) plugin or a command line tool.
Both, when run, analyses the passed code and report warnings to the console about the given code.
Stainless requires and Scala recommends Java SE Development Kit 8.
Newer Java versions won't compile.

\subsection{sbt}
sbt for Scala is like gradle or maven for Java.
It can compile Scala code continously or manual, manage dependencies with support for Maven-formatted repositories, mixing Scala and Java projects and much more.

A simple sbt project has the following structure:
\dirtree{%
  .1 ..
  .2 project.
  .3 build.properties.
  .3 plugins.sbt.
  .2 src.
  .3 main.
  .4 scala.
  .5 Main.scala.
  .2 build.sbt.
}
\emph{build.properties} specifies the abt version used for this project.
If the version is not available locally, sbt will download it.

@@

lazy val root = (project in file("."))
\end{lstlisting}
The project is called root and its source files are located in the files directory.
Executing \code{sbt compile} should now compile the code.

The Stainless webpage has a guide on how to integrate Stainless in an existing project.
The simplifies steps are:
\begin{itemize}
  \item Install an external solver.
  \item Add Stainless sbt plugin to \emph{plugins.sbt}
  \item Enable the plugin in \emph{build.sbt} for the project.
\end{itemize}
After this setup, Stainless will report errors to the console, when running \code{sbt compile}.

@@

Either download a prebuilt JAR file from efpl-lara/stainless GitHub repository or built a binary from source.
The prebuild versions are released by Stainless.
The latest was released on January 14, when there was no support for Scala 2.12.
The 'Bump Scala to 2.12.8' branch was merged on March 4.

>>>>

\section{Configuration}
There are two ways to integrate Stainless in a Scala project, the Scala build tool (sbt) plugin or a command line tool.
Both, when run, analyses the code passed and report warnings to the console about the given code.
Stainless requires and Scala recommends Java SE Development Kit 8.
Newer Java versions won't compile.

\subsection{sbt}
sbt for Scala is like gradle or maven for Java.
It can compile Scala code continuously or manual, manage dependencies with support for Maven-formatted repositories, mixing Scala and Java projects and much more.

A simple sbt project has the following structure:
\dirtree{%
  .1 ..
  .2 project.
  .3 build.properties.
  .3 plugins.sbt.
  .2 src.
  .3 main.
  .4 scala.
  .5 Main.scala.
  .2 build.sbt.
}
\emph{build.properties} specifies the sbt version used for this project.
If the version is not available locally, sbt will download it.

@@

lazy val root = (project in file("."))
\end{lstlisting}
The project is called root and its source files are located in the files' directory.
Executing \code{sbt compile} should now compile the code.

The Stainless web page has a guide on how to integrate Stainless in an existing project.
The simplifies steps are:
\begin{itemize}
  \item Install an external solver.
  \item Add Stainless sbt plugin to \emph{plugins.sbt}
  \item Enable the plugin in \emph{build.sbt} for the project.
\end{itemize}
After this setup, Stainless will report errors to the console, when running \code{sbt compile}.

@@

Either download a prebuilt JAR file from efpl-lara/stainless GitHub repository or built a binary from source.
Prebuild versions are released by Stainless.
The latest was released on January 14, when there was no support for Scala 2.12.
The 'Bump Scala to 2.12.8' branch was merged on March 4.
